Enhancement of SDR in Thessaloniki

### 2024-03-02 GHI_enh_04_investigate.tex
Commit 2024-03-02 11:17

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-03-01}

@@

lmD: 1.566022 +/- 0.1083205

@@

lmD: 0.9508227 +/- 0.1552488

@@

lmD: 1.087008 +/- 0.1678713

@@

lmD: 561.0124 +/- 94.87888

lmY: 561.0217 +/- 94.88053

Arima: 562.031 148.2404 3.7913 1e-04

@@

lmD: 0.003266094 +/- 0.0002706818

@@

lmD: 0.001714795 +/- 0.0002777698

@@

lmD: 0.001677055 +/- 0.00031363

@@

lmD: 0.9770213 +/- 0.1439346

@@

lmD: 0.8175146 +/- 0.1034317

@@

lmD: 0.2160878 +/- 0.03807227

@@

lmD: 0.1909484 +/- 0.03787569

@@

lmD: 24.46426 +/- 2.544261

lmY: 24.46465 +/- 2.544306

Arima: 24.4646 3.0718 7.9642 0

@@

lmD: 0.001335923 +/- 0.0001367163

@@

lmD: 0.000422753 +/- 5.903214e-05

@@

lmD: 0.000372438 +/- 6.132797e-05

@@

lmD: 0.03656094 +/- 0.003621568

@@

lmD: 0.1872432 +/- 0.2494753

@@

lmD: 0.0498083 +/- 0.192504

@@

lmD: 0.0912832 +/- 0.1914519

@@

lmD: 6.13936 +/- 4.224962

lmY: 6.139801 +/- 4.22503

Arima: 6.1407 4.3045 1.4266 0.1537

@@

lmD: 0.0005085756 +/- 0.0002811408

@@

lmD: 0.0003565528 +/- 0.0002141263

@@

lmD: 0.000398809 +/- 0.0002210804

@@

lmD: 0.008776506 +/- 0.00550671

@@

\begin{verbatim}
2024-03-01 16:24:25.3 athan@tyler GHI_enh_04_investigate.R 1.012841 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-03-02}

@@

Units for GLB\_diff.max : Watt/m\^{}2lmD: 1.566022 +/- 0.1083205

@@

Units for GLB\_diff.mean : Watt/m\^{}2lmD: 0.9508227 +/- 0.1552488

@@

Units for GLB\_diff.median : Watt/m\^{}2lmD: 1.087008 +/- 0.1678713

@@

Units for GLB\_diff.sum : J/m\^{}2lmD: 33660.74 +/- 5692.733

lmY: 33661.3 +/- 5692.832

Arima: 33699.7541 8650.717 3.8956 1e-04

@@

Units for GLB\_ench.max : Watt/m\^{}2lmD: 0.003266094 +/- 0.0002706818

@@

Units for GLB\_ench.mean : Watt/m\^{}2lmD: 0.001714795 +/- 0.0002777698

@@

Units for GLB\_ench.median : Watt/m\^{}2lmD: 0.001677055 +/- 0.00031363

@@

Units for GLB\_ench.sum : Watt/m\^{}2lmD: 0.9770213 +/- 0.1439346

@@

Units for GLB\_diff.max : Watt/m\^{}2lmD: 0.8175146 +/- 0.1034317

@@

Units for GLB\_diff.mean : Watt/m\^{}2lmD: 0.2160878 +/- 0.03807227

@@

Units for GLB\_diff.median : Watt/m\^{}2lmD: 0.1909484 +/- 0.03787569

@@

Units for GLB\_diff.sum : J/m\^{}2lmD: 1467.856 +/- 152.6556

lmY: 1467.879 +/- 152.6584

Arima: 1467.8755 184.369 7.9616 0

@@

Units for GLB\_ench.max : Watt/m\^{}2lmD: 0.001335923 +/- 0.0001367163

@@

Units for GLB\_ench.mean : Watt/m\^{}2lmD: 0.000422753 +/- 5.903214e-05

@@

Units for GLB\_ench.median : Watt/m\^{}2lmD: 0.000372438 +/- 6.132797e-05

@@

Units for GLB\_ench.sum : Watt/m\^{}2lmD: 0.03656094 +/- 0.003621568

@@

Units for GLB\_diff.max : Watt/m\^{}2lmD: 0.1872432 +/- 0.2494753

@@

Units for GLB\_diff.mean : Watt/m\^{}2lmD: 0.0498083 +/- 0.192504

@@

Units for GLB\_diff.median : Watt/m\^{}2lmD: 0.0912832 +/- 0.1914519

@@

Units for GLB\_diff.sum : J/m\^{}2lmD: 368.3616 +/- 253.4977

lmY: 368.3881 +/- 253.5018

Arima: 368.4448 258.2729 1.4266 0.1537

@@

Units for GLB\_ench.max : Watt/m\^{}2lmD: 0.0005085756 +/- 0.0002811408

@@

Units for GLB\_ench.mean : Watt/m\^{}2lmD: 0.0003565528 +/- 0.0002141263

@@

Units for GLB\_ench.median : Watt/m\^{}2lmD: 0.000398809 +/- 0.0002210804

@@

Units for GLB\_ench.sum : Watt/m\^{}2lmD: 0.008776506 +/- 0.00550671

@@

\begin{verbatim}
2024-03-02 09:11:28.2 athan@tyler GHI_enh_04_investigate.R 1.451215 mins
\end{verbatim}
